\thetitle

### 2021-03-03 writing/results.tex
touch ups in section 8

Figure~\ref{fig:success-bars} summarizes the overall success rates of
every mode.\footnote{The random mode behaves the same for
all three semantics, so this analysis considers it a single mode.}
The success rates illustrate a few points that underlie the
rest of our analysis.  The first notable piece of information from this
figure is that every mode has failed debugging scenarios, not just
Erasure. This should not come as a surprise to the astute reader.  Running
a mode of the rational programmer on a scenario may result in an exception
that carries no useful information about which module the programmer
should type next. For instance the stack trace of the exception may not
contain frames from any untyped module of the program. This situation can happen at any point
along a blame trail, causing it to fail.

While most failures to debug scenarios follow the above pattern, a few do
not.  Breaking down the failure reasons for Natural blame (1748 in
total) reveals an additional cause. For a small set of debugging scenarios
(40), Natural produces a run time type error blaming a non-buggy
already-typed component. All these cases are due to known open issues with Typed
Racket and class contracts.

In Transient, similar to Natural, most failures are due to unhelpful
exception information (1851 for both Transient first and last blame).
However, Transient also has a substantial number of failures because
scenarios hit the time and memory limits of our experiment
(\textasciitilde770 scenarios).  Additionally, there are nearly 1,000
cases where Transient reports an empty blame set, leaving the rational
programmer without hints about how to proceed.
Sections~\ref{sec:threat:transient} and ~\ref{sec:threat:transient2}
explain both of these causes of failure for Transient in detail and how they affect our
experiment.

@@

In order to better understand the answers the experiment provides for
questions $Q_1$ to $Q_3$, figure~\ref{fig:success-venns} depicts an
analysis of the success of each semantics in comparison to Erasure.
Specifically, the figure shows one Venn diagram per mode of the rational
programmer that uses blame.  Each diagram shows the overlap of successful
scenarios for  the blame mode, its corresponding exception mode, and Erasure.  For
example, the leftmost diagram (Natural) shows that all three modes
succeed on 59.5\% of the  scenarios, only Natural and Natural exceptions
succeed on 25.7\% of the scenarios, only Natural and Erasure succeed on
2.1\%, and Natural alone succeeds on 9.7\%.  This analysis highlights
the success trade-offs each semantics offers against Erasure, with and
without blame. Hence, it answers questions about how to choose to between
blame or just exceptions for each semantics.  For instance, the analysis
for Natural clearly illustrates that, when choosing between Natural blame,
Natural exceptions, and Erasure, Natural blame is the absolutely most
successful: all of the successes of the other two modes are subsets of
Natural's successful scenarios.  On the other hand, Transient's blame
modes fare similarly but the choice is not so clear-cut.

>>>>

Figure~\ref{fig:success-bars} summarizes the overall success rates of
every mode.\footnote{The random mode behaves the same for
all three semantics, so this analysis considers it a single mode.}
The success rates illustrate a few points that underlie the
rest of the analysis.  The first notable piece of information from this
figure is that every mode has failed debugging scenarios, not just
Erasure. This should not come as a surprise to the astute reader.  Running
a rational programmer mode on a scenario may result in an exception
that carries no useful information about which module the programmer
should type next. For instance the stack trace of the exception may not
contain frames from any untyped module of the program. This can happen at any point
along a blame trail, causing it to fail.

While most blame trail failures follow the above pattern, a few do
not.  Breaking down the failure reasons for Natural blame (1748 in
total) reveals an additional cause. For a small set of debugging scenarios
(40), Natural produces a run time type error blaming a non-buggy
already-typed component. All these cases are due to known open issues with Typed
Racket and class contracts.

In Transient, similar to Natural, most failures are due to unhelpful
exception information (1851 for both Transient first and last blame).
However, Transient also has a substantial number of failures because
scenarios hit the time and memory limits of the experiment
(\textasciitilde770 scenarios).  Additionally, there are nearly 1,000
cases where Transient reports an empty blame set, leaving the rational
programmer without hints about how to proceed.
Sections~\ref{sec:threat:transient} and ~\ref{sec:threat:transient2}
explain both of these causes of failure for Transient in detail and how
they affect the
experiment.

@@

In order to better understand the answers the experiment provides for
questions $Q_1$ to $Q_3$, figure~\ref{fig:success-venns} depicts an
analysis of the success of each semantics in comparison to Erasure.
Specifically, the figure shows one Venn diagram per mode of the rational
programmer that uses blame.  Each diagram shows the overlap of successful
scenarios for  the blame mode, its corresponding exception mode, and Erasure.  For
example, the leftmost diagram (Natural) shows that all three modes
succeed on 59.5\% of the  scenarios, only Natural and Natural exceptions
succeed on 25.7\% of the scenarios, only Natural and Erasure succeed on
2.1\%, and Natural alone succeeds on 9.7\%.  This analysis highlights
the success trade-offs each semantics offers against Erasure, with and
without blame. For instance, the analysis
for Natural clearly illustrates that, when choosing between Natural blame,
Natural exceptions, and Erasure, Natural blame is the absolutely most
successful: all of the successes of the other two modes are subsets of
Natural's successful scenarios.  On the other hand, Transient's blame
modes fare similarly but the choice is not so clear-cut.
